% Created 2018-01-09 Tue 18:01
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\author{ATORELLO}
\date{\textit{<2016-10-24 Mon>}}
\title{LAB JOURNAL - DAILY BENCH WORK}
\hypersetup{
 pdfauthor={ATORELLO},
 pdftitle={LAB JOURNAL - DAILY BENCH WORK},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 24.3.1 (Org mode 9.0.1)}, 
 pdflang={Language, E.G. ‘En’ (Org-Export-Default-Language)}}
\begin{document}

\maketitle
\tableofcontents

\section{Barcoded libraries}
\label{sec:orgd4745f1}
\subsection{Barcoding PCR}
\label{sec:org4b6e281}
The first step is to do the barcoding PCR according to this protocol:\\
\begin{center}
\begin{tabular}{l}
\hline
Reagent\\
\hline
10 ng plasmid\\
2.5 uL primer GAT155\\
2.5 uL primer GAT385\\
10 uL GC buffer 10x\\
1 uL dNTPs\\
0.5 uL Phusion Polymerase\\
32.5 uL water\\
\hline
\end{tabular}
\end{center}

with this programme:\\
\begin{center}
\begin{tabular}{ll}
\hline
T & Time\\
\hline
98C & 2 min\\
98C & 15 sec\\
60C & 20 sec\\
72C & 5 min\\
x28 cycles & \\
72C & 2 min\\
\hline
\end{tabular}
\end{center}

Check the outcome of PCR with 1\% agarose gel.\\

\subsection{DpnI digestion}
\label{sec:orgd47708b}
The recipe is:\\
\begin{center}
\begin{tabular}{l}
\hline
Reagent\\
\hline
45 uL BCR PCR product\\
5 uL CutSmart Buffer 10x\\
1 uL DpnI enzyme\\
\hline
\end{tabular}
\end{center}

1h at 37C and 20 min at 80C.\\

\subsection{MinElute kit purification}
\label{sec:orgc9ff965}
\begin{enumerate}
\item Add 5 volumes of PB buffer for 1 volume of PCR product and 10 uL of NaAc 3M.\\
\item Put the column in a 2 mL collection tube.\\
\item Spin the column 1 min at 13,000 rpm and discard the flow-through\\
\item Add 750 uL of PE buffer and spin at 13,000 rpm for 1 min. Discard the flow-through\\
\item Spin for 2 min and replace the collection tube (1 mL tube)\\
\item Elute in 10+10 uL EB buffer. Wait 5 min and spin for 1 min.\\
\end{enumerate}

\subsection{Gibson Cloning}
\label{sec:orgac24f5c}
\begin{enumerate}
\item 5 uL of template DNA\\
\item 5 uL water\\
\item 10 uL Gibson mix\\
\end{enumerate}

1h at 50C\\

\subsection{EtOH Purification}
\label{sec:orgd34d048}
\begin{enumerate}
\item Add 2.5 V of EtOH\\
\item Add 1/10 of NaAc 3M and 2 uL of glycogen\\
\item Immerse in EtOH + carbonic niege to freeze and precipitate DNA\\
\item Spin for 30 min at 16,000 rpm at 4C\\
\item Discard the supernatant\\
\item Wash the pellet with 75\% EtOH and spin for 10 min at 16,000 rpm at 4C\\
\item Ressuspend the pellet in 10 uL of water.\\
\end{enumerate}

\subsection{Transformation of high electrocompetent E. coli cells}
\label{sec:orga2c64ae}
\begin{enumerate}
\item Thaw the alliquot of E. coli in ice\\
\item In 0.1 cm cuvettes, pipette 25 uL of E. coli suspension and 2.5 uL of purified plasmid\\
\item Electroporate with the corresponding programme\\
\item Add 1 mL of recovery medium (aka SOC media)\\
\item Pool the transformed cells in a 15 mL falcon\\
\item Prepare 3 LB + Amp agar plates and a seriate dilution of the culture (1/1000,1/2000,1/4000):\\
\end{enumerate}

\begin{center}
\begin{tabular}{lll}
\hline
Dilution & Culture volume & Final volume\\
\hline
1/1000 &  & 200 uL\\
1/2000 &  & 200 uL\\
1/4000 &  & 200 uL\\
\hline
\end{tabular}
\end{center}

Plate this 200 uL in this plates and culture overnight at 37C.\\

\begin{enumerate}
\item Transfer the rest of the culture into 500 mL of liquid LB+Amp 1x (500 uL) and culture ON at 37C.\\
\end{enumerate}

\subsection{MaxiPrep NucleoBond Xtra Midi kit}
\label{sec:orgdecb077}
\begin{enumerate}
\item Culture E. coli cells at 37C and at 180 rpm overnight.\\
\item Harvest cells and centrifuge at 4500g at 4C for 15 min.\\
\item Ressuspend the pellet in 12 mL of RES buffer, add 12 mL LYS buffer and wait 5 min at RT.\\
\item Equilibrate the column with 25 mL of EQU buffer.\\
\item Add 12 mL of NEU buffer to the lysate.\\
\item Mix the tube and load the lysate into the column.\\
\item 1st wash. Add 15 mL of buffer EQU.\\
\item Discard the filter.\\
\item 2nd wash. Add 25 mL of buffer WASH.\\
\item Add 25 mL of ELU buffer.\\
\item Add 10.5 mL of isopropanol, vortex and centrifuge at 4000 rpm for 1h at 4C.\\
\item Discard the supernatant and add 4 mL of 70\% EtOH and centrifuge at 4000 rpm at 4C for 15 min.\\
\item Discard the supernatant and ressupend the pellet in 100 uL of nuclease-free water.\\
\item Quantify the library in a Nanodrop and leave the prep at 1ug/mL.\\
\end{enumerate}

\begin{center}
\begin{tabular}{lll}
\hline
conc ng/uL & 260/280 & 260/230\\
\hline
 &  & \\
\hline
\end{tabular}
\end{center}

\subsection{PureLink™ HiPure Plasmid MaxiPrep kit (Invitrogen)}
\label{sec:org071bde7}
\begin{enumerate}
\item \textbf{Equilibrate}. Add 30 mL Equilibration Buffer (EQ1) to the column and allow the solution to drain\\
\end{enumerate}
by gravity flow.\\

\begin{enumerate}
\item \textbf{Harvest} . Centrifuge the the culture at 4500g for 15 min at 4C. Discard all the medium.\\

\item \textbf{Resuspend}. Add 10 mL Resuspension Buffer (R3) with RNase A to the cell pellet and ressupend\\
\end{enumerate}
until it is homogenous.\\

\begin{enumerate}
\item \textbf{Lyse}. Add 10 mL Lysis Buffer (L7). Mix gently by inverting the capped tube until the mixture is\\
\end{enumerate}
homogeneous. Do not vortex. Incubate at room temperature for 5 minutes.\\

\begin{enumerate}
\item \textbf{Precipitate}. Add 10 mL Precipitation Buffer (N3). Mix immediately by inverting the tube\\
\end{enumerate}
until the mixture is homogeneous. Do not vortex.\\

\begin{enumerate}
\item \textbf{Bind}. Load the lysate onto the equilibrated column. Allow the solution in\\
\end{enumerate}
the column to drain by gravity flow.\\

\begin{enumerate}
\item \textbf{Wash}. Add 60 mL Wash Buffer (W8) to the column. Discard the flow‐through after\\
\end{enumerate}
Wash Buffer (W8) drains from the column.\\

\begin{enumerate}
\item \textbf{Elute}. Place a sterile 50-mL centrifuge tube under the column. Add 15 mL\\
\end{enumerate}
Elution Buffer (E4) to the column. Allow the solution to drain by gravity\\
flow. The elution tube contains the purified DNA.\\

\begin{enumerate}
\item \textbf{Precipitate and Wash}. Add 10.5 mL isopropanol to the eluate. Mix well. Centrifuge the tube at\\
\end{enumerate}
>12,000 × g for 30 minutes at 4°C. Discard the supernatant.\\
Wash the pellet in 5 mL 70\% ethanol. Centrifuge the tube at >12,000g for 5 minutes at 4°C.\\
Discard the supernatant.\\

\begin{enumerate}
\item \textbf{Resuspend}. Air-dry the pellet for 10 minutes, then resuspend the purified plasmid\\
\end{enumerate}
DNA in 200–500 uL of water. Store at -20C.\\

\begin{enumerate}
\item \textbf{Quantification}. Check the yield of extraction. Dilute until 1ug/uL.\\
\end{enumerate}
\begin{center}
\begin{tabular}{lll}
\hline
conc ng/uL & 260/280 & 260/230\\
\hline
 &  & \\
\hline
\end{tabular}
\end{center}

\section{Cell culture}
\label{sec:orgff5e73c}
Cells grow at 25C with Schneider's Drosophila medium supplemented with 5\% FBS.\\

To pass the cells, I take 5 mL of the culture + 15 mL of medium.\\

\section{Transfection of Kc167 cells by electroporation}
\label{sec:orgcf1c1aa}
They are needed 20 milions cells per transfection.\\
\begin{enumerate}
\item Prepare as much plates as you need (1 plate for transfection) in order to get 20 milions cells at the day of transfection.\\
\item Spin cells at 800g for 3 min.\\
\item Remove the supernatant and resuspend the cells in 800 uL x number of transfections.\\
\item Pipette 20 ug of DNA in an electroporation cuvette (Biorad, 0.4 cm gap).\\
\item Add 800 uL of cell suspension and pipette up \& down 2-3 times.\\
\item Electroporate at 1000 uF and 250 V.\\
\item Wait 5 min\\
\item Transfer the cells into a 10 cm dish containing 10 mL of Schneider medium + 5\% FBS previously warmed at RT.\\
\item Grow cells at 23C.\\
\end{enumerate}

\section{Freeze Kc167 cells}
\label{sec:org50f750f}
\begin{enumerate}
\item Spin cells at 200g for 5 min.\\
\item Ressuspend the cells with 1 or 2 mL of medium + 10\% DMSO. Do 2 CryoVials per biological replicate.\\
\item Put at the isopropanol tank at -80 C overnight.\\
\item Place the cells at liquid nitrogen.\\
\end{enumerate}

\section{Thaw Kc 167 cells}
\label{sec:org23ae3bc}
\begin{enumerate}
\item Take the cells from the liquid nitrogen tank.\\
\item Rapidly thaw vial in 37°C water bath.\\
\item Prepare a 15mL falcon with 10 mL of medium.\\
\item Take 500 uL from the cell suspension and transfer to the 15 mL falcon.\\
\item Take 500 uL from the falcon and add to the cryovial. Pipette up and down.\\
\item Transfer 500 uL to the falcon, pipette up and down.\\
\item Put the rest of cell suspension in the falcon.\\
\item Spin cells at 200g for 7 min, discard the supernatant and ressupend in 1-2 mL of fresh medium.\\
\item Culture the cells in a T25 flask until confluence.\\
\item Pass the cells in a 10 cm dish until confluence.\\
\item Pass the cells in a T75 flask.\\
\end{enumerate}
\section{FACS sorting of double positive (GFP \& mCherry) Kc167 cells}
\label{sec:orgaa91c0a}
\begin{enumerate}
\item Count cells\\
\item Spin cells at 200g for 7 min.\\
\item Ressupend them in x mL of medium + P/S (final concentration: 10 milion/mL).\\
\item Add 1uL/mL DAPI.\\
\end{enumerate}

\section{Kc167 conditioned medium}
\label{sec:org2e788e6}
\begin{enumerate}
\item Spin the culture at 200g for 5 min\\
\item Take the supernatant and filter it with a 45 um filter carefully.\\
\item Dilute the filtrate 1:1 with fresh Schneider Medium.\\
\item Store at 4C.\\
\end{enumerate}

\section{gDNA extraction with DNeasy Tissue \& Blood kit}
\label{sec:org6b07f33}
\begin{enumerate}
\item Take 15-20 milion cells\\
\item Add 5mL of cold PBS and harvest cultures 5 min at 300 g\\
\item Discard the supernatant\\
\item Add 5 mL of cold PBS and ressupend the cells\\
\item Spin cells at 300 g for 5 min and discard the supernatant\\
\item Put the pellets on ice\\
\item Ressupend in mix solution:\\
\end{enumerate}
\begin{center}
\begin{tabular}{lr}
\hline
Component & uL\\
\hline
ice cold PBS & 200\\
Proteinase K & 20\\
RNase H & 4\\
\hline
\end{tabular}
\end{center}

Set the suit master mix.\\

\begin{enumerate}
\item Add 200 uL of AL buffer. Mix thoroughly by pipetting.\\
\item Incubate samples at 56C for 10 min.\\
\item Add 200 uL absolute ethanol and mix throroughly by pipetting.\\
\item Pipet the mixture into a DNeasy Mini spin column placed in a 2 mL\\
\end{enumerate}
collection tube. Centrifuge at ≥ 6000 x g (8000 rpm) for 1 min. Discard\\
the flow-through and collection tube.\\
\begin{enumerate}
\item Place the spin column in a new 2 ml collection tube. Add 500 ul\\
\end{enumerate}
Buffer AW1. Centrifuge for 1 min at ≥6000 x g. Discard the flow-through\\
and collection tube.\\
\begin{enumerate}
\item Place the spin column in a new 2 ml collection tube, add 500 ul\\
\end{enumerate}
Buffer AW2, and centrifuge for 2 min + 1 min at 20,000 x g (14,000 rpm). Discard\\
the flow-through and collection tube.\\
\begin{enumerate}
\item Transfer the spin column to a new 1.5 ml or 2 ml microcentrifuge tube.\\
\item Elute the DNA by adding 200 ul Buffer AE to the center of the spin column\\
\end{enumerate}
membrane. Incubate for 1 min at room temperature (15–25°C). Centrifuge\\
for 1 min at ≥6000 x g. Do it again.\\
\end{document}